### 2023-02-20 paper.tex
Initial commit with references

\documentclass[twoside]{article}
\usepackage{seminarpaper}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{csquotes}

\addbibresource{references.bib}

\begin{document}

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

\twocolumn[

\papertitle{Transformers in Language Models}

\paperauthor{Mikael Fredriksson}

\paperaddress{ } ]

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points.  The {\bf Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

\section{Introduction}
This paper will take a look at three popular language models utilizing
transformers in their architecture. It will also give a quick overview
of some applications and additions to the generic model.

\section{Models}

The models this paper discusses very closely follow the initial architecture
presented in the paper originally proposing the transformer 
\cite{vaswani_attention_2017}. Most of the differences between 
the models come down to training.

\subsection{Generative Pre-Trained Transformer}
Generative Pre-Trained Transformer, henceforth referred to as GPT, is a model
which is focused mostly on text generation \cite{brown_language_2020}. 
GPT uses only the decoder of the transformer with 12 layers 
\cite{radford_improving_nodate}. The training is split into unsupervised
pre-training and supervised fine-tuning.

In the unsupervised pre-training phase, the model is given a set of long form text
\cite{radford_improving_nodate}. The supervised fine-tuning is used to train the
model for a specific task.

As the number of parameters in the model grows past a certain threshold, it
is no longer necessary to fine-tune the model for each specific use case 
\cite{brown_language_2020}. Depending on the task at hand, it might be sufficient
to just give the model some examples of the task initially and it will (understand what you want it to do). The examples are given to
the model after training during inference and thus differs from fine-tuning. 
This is called few-shot learning. Special cases of this are one-shot learning which is
otherwise similar to few-shot learning except the number of examples is one.
Zero-shot learning refers to giving the task description using natural language,
kind of like you were explaining it to a human.

As an example \cite{brown_language_2020} used English to French translation.
The researchers gave the model between 10 to 100 pairs of examples of the
same sentence in English and French. The last pair had just an English sentence
and the model was expected to produce the corresponding sentence translated into
French.

While few-shot learning requires less data and computing power, which makes it more
accessible compared to fine-tuning a large model, at least during the writing of 
\cite{brown_language_2020} failed to produce comparable results to fine-tuning.
The number of examples given is restricted by the size of the model's context,
which for GPT-3 was 2048 tokens, around 1500 words (citation needed, pricing page has this info).

\subsection{Bidirectional Encoder Representations from Transformers}

\subsection{Text-to-Text Transfer Transformer}

\section{Applications}

\subsection{Toolformer}
Transformers can be taught to use different tools \cite{schick_toolformer_2023}. 
This can be achieved using additional fine tuning, as is the case with Toolformer
\cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
about the tools available to it, as in Toolformer Zero \cite{markus_toolformer_2023}.

\printbibliography

\end{document}

### 2023-02-20 sample_paper.tex
Initial commit with references

\documentclass[twoside]{article}
\usepackage{seminarpaper}

\begin{document}

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

\twocolumn[

\papertitle{Instructions for seminar papers}

\paperauthor{ Author }

\paperaddress{ } ]

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points.  The {\bf Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

\section{GENERAL FORMATTING INSTRUCTIONS}

Papers are in 2 columns with the overall line width of 6.75~inches (41~picas). Each column is 3.25~inches wide (19.5~picas).  The space
between the columns is .25~inches wide (1.5~picas).  The left margin is 1~inch (6~picas).  Use 10~point type with a vertical spacing of
11~points. Times Roman is the preferred typeface throughout.

Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.  Top rule is 4~points thick and bottom rule is 1~point thick.
Allow 1/4~inch space above and below title to rules.

Author descriptions are center-justified, initial caps.

One-half line space between paragraphs, with no indent.

\section{FIRST LEVEL HEADINGS}

First level headings are all caps, flush left, bold, and in point size
12. One line space before the first level heading and 1/2~line space
after the first level heading.

\subsection{Second Level Heading}

Second level headings are initial caps, flush left, bold, and in point
size 10. One line space before the second level heading and 1/2~line
space after the second level heading.

\subsubsection{Third Level Heading}

Third level headings are flush left, initial caps, bold, and in point
size 10. One line space before the third level heading and 1/2~line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps, bold, and
Roman type.  One line space before the fourth level heading, and
place the section text immediately after the heading with, no line
break, but an 11 point horizontal space.

\subsection{CITATIONS, FIGURES, REFERENCES}

\subsubsection{Citations in Text}

Citations within the text should include the author's last name and
year, e.g., (Cheesman, 1985). References should follow any style that
you are used to using, as long as their style is consistent throughout
the paper.  Be sure that the sentence reads correctly if the citation
is deleted: e.g., instead of ``As described by (Cheesman, 1985), we
first frobulate the widgets,'' write ``As described by Cheesman
(1985), we first frobulate the widgets.''  Be sure to avoid
accidentally disclosing author identities through citations.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Use 8 point type for footnotes. Place the
footnotes at the bottom of the column in which their markers appear,
continuing to the next column if required. Precede the footnote
section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
long.\footnote{Sample of the second footnote.}

\subsubsection{Figures}

All artwork must be centered, neat, clean, and legible.  All lines
should be very dark for purposes of reproduction, and art work should
not be hand-drawn.  Figures may appear at the top of a column, at the
top of a page spanning multiple columns, inline within a column, or
with text wrapped around them, but the figure number and caption
always appear immediately below the figure.  Leave 2 line spaces
between the figure and the caption. The figure caption is initial caps
and each figure should be numbered consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page rather than
splitting the figure and figure caption.
\begin{figure}[h]
\vspace{.3in}
\centerline{\fbox{This figure intentionally left non-blank}}
\vspace{.3in}
\caption{Sample Figure Caption}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables. Table number and title always appear above the table.
See Table~\ref{sample-table}.

One line space before the table title, one line space after the table title, and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[h]
\caption{Sample Table Title} \label{sample-table}
\begin{center}
\begin{tabular}{ll}
{\bf PART}  &{\bf DESCRIPTION} \\
\hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\subsubsection*{Acknowledgements}

Use unnumbered third level headings for the acknowledgements.  All
acknowledgements go at the end of the paper.  Be sure to omit any
identifying information in the initial double-blind submission!

\subsubsection*{References}

References follow the acknowledgements.  Use an unnumbered third level
heading for the references section.  Any choice of citation style is
acceptable as long as you are consistent.  Please use the same font
size for references as for the body of the paper---remember that
references do not count against your page length total.

J.~Alspector, B.~Gupta, and R.~B.~Allen (1989). Performance of a
stochastic learning microchip.  In D. S. Touretzky (ed.), {\it
  Advances in Neural Information Processing Systems 1}, 748-760.  San
Mateo, Calif.: Morgan Kaufmann.

F.~Rosenblatt (1962). {\it Principles of Neurodynamics.} Washington,
D.C.: Spartan Books.

G.~Tesauro (1989). Neurogammon wins computer Olympiad.  {\it Neural
  Computation} {\bf 1}(3):321-323.

\end{document}

### 2023-02-23 paper.tex
Write about bert

@@
 \subsection{Generative Pre-Trained Transformer}
-Generative Pre-Trained Transformer, henceforth referred to as GPT, is a model
+Generative Pre-Trained Transformer, more commonly known as GPT, is a model
 which is focused mostly on text generation \cite{brown_language_2020}. 
@@
 \subsection{Bidirectional Encoder Representations from Transformers}
+Bidirectional Encoder Representations from Transformers, henceforth referred to as BERT,
+is a language model utilizing masking of words during training to achieve bidirectionality
+in the model. \cite{devlin_bert_2019}
+
+BERT uses a similar architecture as the original transformer. It uses the encoder with
+multiple layers. The main difference is in the training methods. In the pre-training step,
+two different training approaches are used: masked language model and next sentence prediction.
+Masking allows the self-attention layer to take into account both sides of a given word, instead
+of just one side, as in GPT which can only use the previous words as context. Using next sentence
+prediction improves the model's understanding of the relationships between sentences. This is
+useful for question answering and natural language inference type of tasks. \cite{devlin_bert_2019}
+
+A masked language model (MLM) is achived by hiding a certain number of tokens, 12\% in the paper, and
+asking the model to predict the hidden token. The model can then use both sides of the token as
+context. Some of the tokens marked for masking are instead turned 
+into random tokens or kept as is. This helps prevent a difference between pre-training and fine-tuning.
+Other unidirectional methods predict the entire text during training while MLM only 
+does so only for the masked tokens. \cite{devlin_bert_2019}
+
+Next sentence prediction takes a pair of sentences, \texttt{A} and \texttt{B}, and requests the model
+to predict whether \texttt{B} follows \texttt{A} or not. In the paper, 50\% of the time \texttt{B} 
+was the next sentence and 50\% of the time it was not. \cite{devlin_bert_2019}
+
+BERT also uses unsupervised pre-training and supervised fine-tuning as the general training setup \cite{devlin_bert_2019}.
+The largest amount of work and time is spent pre-training the model on a large set of unstructured
+text. This teaches the model general language understanding. Fine-tuning can then be used to 
+train the model for specific natural language tasks leveraging the existing language knowledge 
+from the pre-training stage. Fine-tuning is usually a more lightweight operation than pre-training.
 

### 2023-02-23 paper.tex
Recreate t5 picture

@@
 \usepackage{csquotes}
+\usepackage{tikz}
+
+\usetikzlibrary{positioning}
+\usetikzlibrary{matrix}
 
@@
 of some applications and additions to the generic model.
+
+TODO: explain why I chose these specific models to look at maybe?
+
+\section{Training}
+TODO: write about transfer learning in general, take from bert.
+means big pretraining and then using that strong understanding
+to fine tune for specific tasks
 
@@
 \subsection{Text-to-Text Transfer Transformer}
+\begin{tikzpicture}[line width=0.3mm, align=center, font=\sffamily]
+  % Nodes
+  \matrix [matrix of nodes, row sep=2mm] (rightmat) {
+    \node (translatein) [rounded corners=3pt, draw, fill=green!20] {"translate English to German: That is good."}; \\
+    \node (colain)[rounded corners=3pt, draw, fill=red!20] {"cola sentence: The\\course is jumping well."}; \\
+    \node (stsbin)[rounded corners=3pt, draw, fill=yellow!20] {"stsb sentence1: The rhino grazed\\on the grass. sentence2: A rhino\\is grazing in a field."}; \\
+    \node (summaryin)[rounded corners=3pt, draw, fill=cyan!20] {"summarize: state authorities\\dispatched emergency crews tuesday to\\survey the damage after an onslaught\\of severe weather in mississippi..."}; \\
+  };
+  \node [right=of rightmat, rounded corners=3pt, draw, fill=gray!20] (t5) {\Huge T5};
+  \matrix [matrix of nodes, right=of t5, row sep=2mm] {
+    \node (translateout)[rounded corners=3pt, draw, fill=green!20] {"Das ist gut."}; \\
+    \node (colaout)[rounded corners=3pt, draw, fill=red!20] {"not acceptable"}; \\
+    \node (stsbout)[rounded corners=3pt, draw, fill=yellow!20]  {"3.8"}; \\
+    \node (summaryout)[rounded corners=3pt, draw, fill=cyan!20] {"six people hospitalized after\\a storm in attala county."}; \\
+  };
+
+  % Lines
+  \draw [-] (translatein.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
+  \draw [-] (colain.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
+  \draw [-] (stsbin.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
+  \draw [-] (summaryin.east) .. controls +(right:5mm) and +(left:5mm) .. (t5.west);
+
+  \draw [-] (translateout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
+  \draw [-] (colaout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
+  \draw [-] (stsbout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
+  \draw [-] (summaryout.west) .. controls +(left:5mm) and +(right:5mm) .. (t5.east);
+\end{tikzpicture}
 

### 2023-03-06 paper.tex
Add text and todos

@@
 transformers in their architecture. It will also give a quick overview
-of some applications and additions to the generic model.
+of some applications and additions to the generic model. The aim is to
+give the reader a general overview of the current landscape of different
+transformer based language model architectures and some example applications.
 
-TODO: explain why I chose these specific models to look at maybe?
+The three different models are all similar in architecture being mostly
+faithful to the original transformer architecture as presented in 
+\cite{vaswani_attention_2017}. However, each of them have a different approach
+to using the decoder and encoder stacks of the transformer. GPT uses only
+the decoder, BERT only the encoder and T5 both encoder and decoder
+\cite{radford_improving_nodate,devlin_bert_2019,raffel_exploring_2020}.
 
 \section{Training}
-TODO: write about transfer learning in general, take from bert.
-means big pretraining and then using that strong understanding
-to fine tune for specific tasks
+All three of the models this paper discusses use transfer learning for 
+training. The general idea is to first train a baseline model unsupervised 
+using a large amount of unstructured text and then fine tuning the model
+for each specific task after.
+
+The objective of the unsupervised pre-training stage is to teach the model
+general language understanding. The exact details between models varies but
+in general, a massive number tokens are fed into to model during the course
+of training. Each word corresponds to a single or a few tokens depending on 
+the encoding used [citation needed, same as pricing] and the number of tokens
+used in training can go up to the trillions \cite{raffel_exploring_2020}. 
+The model is asked to predict a missing token based on context.
+
+In the fine-tuning stage, the pre-trained model is used as a baseline. A new
+model is trained using supervised learning with a task specific data set. 
+The training can fine-tune all the parameters of the model, as in BERT 
+\cite{devlin_bert_2019}, or an additional layer can be added and then
+trained, as in GPT \cite{radford_improving_nodate}.
 
@@
 the models come down to training.
+
+TODO: talk about masking the attention layers somewhere, was talked about in
+the t5 paper
+
+TODO: talk about the exact differences between fine-tuning,
+i think bert modifies the weights and gpt only adds an extra layer after
+
+TODO: elmo for feature based?
 
@@
 \subsection{Text-to-Text Transfer Transformer}
+\begin{figure*}
+  \centering
   \begin{tikzpicture}[line width=0.3mm, align=center, font=\sffamily]
@@
   \end{tikzpicture}
+  \caption{Illustrating the types of inputs and outputs. Recreated from \cite{raffel_exploring_2020}.}
+\end{figure*}
+
+Text-to-Text Transfer Transformer, abbreviated as T5, is a language model modelling each
+task as text in, text out. It uses both the encoder and decoder layers of the transformer.
+\cite{raffel_exploring_2020}
+
+The main differentiating factor of T5 is the way it chooses to model tasks. Instead of 
+tailoring each output to the specific task at hand, every task takes in a text prefix
+describing the task and outputting the results as text. For example, for STS-B classification
+task the model is trained to out one of a set of floating point numbers 
+$x \in \{ 1+0.2k \mid k \in \{ 0, 1, ..., 20\} \}$ as a text. Many other models just 
+output a number directly as a sliding scale from 1 to 5.
 
@@
 \subsection{Toolformer}
-Transformers can be taught to use different tools \cite{schick_toolformer_2023}. 
+Transformers are able to produce very natural text but they struggle with seemingly
+simple tasks such as simple mathematical calculations and factual information gathering.
+To get around of these limitations, transformers can be taught to use external tools
+to offload these tasks to applications better suited to them. \cite{schick_toolformer_2023} 
 This can be achieved using additional fine tuning, as is the case with Toolformer
@@
 
+TODO: maybe an example here about asking chat gpt about a recent event leading to hallucination
+and/or asking about a simple mathematical calculation leading to the wrong result
+
 \printbibliography

### 2023-03-09 paper.tex
Write some examples about problems

@@
 trained, as in GPT \cite{radford_improving_nodate}.
+
+\subsection{Vocabulary}
+Different model architectures use different vocabularies. These are chosen based
+on the differing requirements of the models. The vocabulary needs to accommodate 
+multiple languages and proper nouns while using as few tokens as possible per word.
+Memory usage also has to be balanced and the number of tokens cannot grow infinitely
+large.
 
@@
 
-TODO: maybe an example here about asking chat gpt about a recent event leading to hallucination
-and/or asking about a simple mathematical calculation leading to the wrong result
+For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
+GPT-3.5 [citation needed], to do a simple calculation, it answers confidently. 
+With a prompt of "\texttt{what is 491*397}" we receive a response of 
+"\texttt{The product of 491 and 397 is 195127.}". Unfortunately, using a calculator
+leads to a different answer: 194927. Dangerously close, but not quite there.
+
+Another example is asking the model about something they have not been trained on, for
+example about future events. Prompting the model with 
+"\texttt{What did Sauli Niinistö accomplish during his third term in office?}" returns
+a logically perplexing response "\texttt{Sauli Niinistö is the current President of Finland, 
+and he is currently serving his second consecutive term in office. 
+His third term began on March 1, 2018, and it will end on February 28, 2024. ...}".
+The response claims that Sauli Niinistö is currently serving his second term in office
+which is correct as of 2023 and also in 2021 where the training data of GPT-3.5 ends 
+[citation needed]. However, after this, the response claims that his third term began
+in 2018, directly contradicting the previous statement. It is also important to mention
+that there has been a two term limit since (insert year here) written into law 
+[citation needed, finlex?]. Rest of the response after the first paragraph is removed.
+
+While these limitations can be quite clear to professionals, many people without relevant
+experience have no way of discerning factually correct answers from wrong ones. The confidence
+by which the models answer can also mislead people into trusting the answers too much.
+
+\section{Problems}
+TODO: write about hallucination, overconfidence, radicalization etc.
 

### 2023-03-10 paper.tex
Write about palm-e

@@
 \subsection{Toolformer}
-Transformers are able to produce very natural text but they struggle with seemingly
+Transformers are able to produce very natural text but as previously mentioned, they struggle with seemingly
 simple tasks such as simple mathematical calculations and factual information gathering.
@@
 
+\subsection{Multimodal Models}
+Large language models have proven themselves very capable at a variety of language related
+tasks. Their usefulness quickly diminishes the further we stray from their training set.
+Using multimodal models (check name) however, we can widen the area of tasks the model
+can complete and even achieve positive transfer, benefitting from the variety of tasks
+it is trained for \cite{driess_palm-e_2023}.
+
+PaLM-E is a multimodal language model utilizing a transformer based language model called
+PaLM \cite{chowdhery_palm_2022,driess_palm-e_2023}. Multimodality refers to the fact that
+the models accept types of input other than text. For example, PaLM-E accepts an input like
+"\texttt{Q: What happened between <img\_1> and <img\_2>?}" \cite{driess_palm-e_2023} where
+\texttt{<img\_1>} and \texttt{<img\_2>} refer to image embeddings. The E in PaLM-E refers to
+the model being embodied. This means that the model is capable of performing tasks that
+relate to real world objects. For example, the model can be used to plan high-level tasks
+for a robot. \cite{driess_palm-e_2023}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics*[scale=0.1]{img/palm-e-transfer.png}
+  \caption{
+    PaLM-E displays positive transfer in learning. The performance is better for these three
+    distinct robotics domains when trained together than when trained separately for the 
+    specific tasks. \cite{driess_palm-e_2023}
+  }
+\end{figure}
+
+\section{Problems}
+TODO: write about hallucination, overconfidence, radicalization etc.
 For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
@@
 
-\section{Problems}
-TODO: write about hallucination, overconfidence, radicalization etc.
-
 \printbibliography

### 2023-03-10 paper.tex
Add references and todo

@@
 
-The models this paper discusses very closely follow the initial architecture
+The models this paper discusses closely follow the initial architecture
 presented in the paper originally proposing the transformer 
 \cite{vaswani_attention_2017}. Most of the differences between 
-the models come down to training.
+the models come down to training, attention layer masking and the encoder-decoder layers
+\cite{raffel_exploring_2020}.
 
@@
 the t5 paper
+TODO: talk about masking, t5 paper lists this as the biggest differentiating factor
+between models. the t5 paper is also good source for general comparison between different
+architectures and approaches
+(the above two are the same)
 

### 2023-03-13 paper.tex
Write about attention masking

@@
 \documentclass[twoside]{article}
+\usepackage[english]{babel}
 \usepackage{seminarpaper}
@@
 
+\subsection{Attention masking}
+
+TODO: explain how attention masking works
+
+TODO: explain sparse transformer, used in gpt-3 (maybe 2 also)
+
+The original transformer's encoder-decoder architecture as specified in 
+\cite{vaswani_attention_2017} corresponds to the leftmost masking pattern as
+specified in \ref{masking_patterns}. T5 uses this architecture and masking pattern
+\cite{raffel_exploring_2020}. As previously mentioned, BERT uses an encoder
+only architecture \cite{devlin_bert_2019} and uses a fully-visible masking 
+pattern with a special classification token \cite{raffel_exploring_2020}. GPT on
+the other hand, uses a decoder only architecture \cite{radford_improving_nodate}
+and uses causal masking \cite{liu_generating_2018}.
+
+Prefix masking can be useful for example when translating. The prefix allows the
+model to attend to the entire source language sentence and causal masking can be 
+used only for the target language sentence prediction. \cite{raffel_exploring_2020}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics*[scale=0.15]{img/attention_masking.png}
+  \caption{
+    Different attention masking patterns seen in transformer based language models.
+    Dark squares indicate that the attention mechanism can see the input $i$ at time $j$.
+    Light squares indicate that the access is blocked for a given pair $i$, $j$. 
+    \cite{raffel_exploring_2020}
+  }
+\end{figure}
+\begin{figure}[h]
+  \centering
+  \includegraphics*[scale=0.15]{img/lm_masking.png}
+  \caption{
+    Different masking patterns used within language models. Dark lines correspond to 
+    fully-visible masking. Light gray lines indicate causal masking.
+    \cite{raffel_exploring_2020}
+  }
+\end{figure}
+\label{masking_patterns}
+
+TODO: remake, text not visible
+\begin{figure}[h]
+  \centering
+  \includegraphics*[scale=0.1]{img/sparse_transformer.png}
+  \caption{
+    \cite{child_generating_2019}
+  }
+\end{figure}
+
 \subsection{Vocabulary}
@@
 TODO: elmo for feature based?
+
+TODO: talk about GPT sparse transformer, used in gpt-3
 
@@
 \cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
-about the tools available to it, as in Toolformer Zero \cite{markus_toolformer_2023}.
+about the tools available to it, as in Toolformer Zero \cite{minosvasilias_markus_toolformer_2023}.
 

### 2023-03-16 paper.tex
Initial final content

@@
 \addbibresource{references.bib}
+
+% TODO: temporary for having the "for the reader" section start from 0
+\setcounter{section}{-1}
 
@@
 \begin{abstract}
-  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
-  both left and right-hand margins. Use 10~point type, with a vertical
-  spacing of 11~points.  The {\bf Abstract} heading must be centered,
-  bold, and in point size 12. Two line spaces precede the
-  Abstract. The Abstract must be limited to one paragraph.
+  This paper discusses three language models based on the transformer architecture.
+  I aim decipher some differences between the models which seem very similar at first glance.
+  The paper also takes a look at some applications and extensions to basic language
+  models and some problems present in large language models, including biases
+  and hallucination.
 \end{abstract}
+
+\section{For the reader}
+There's a bit of length left in this paper for some extra explanations,
+examples and images, so if there's anything specific you would like to
+read about, please indicate that in your review. It can be quite hard to 
+gauge the level of difficulty of different topics after being submerged 
+in them for a while. Please keep in mind that I should not overlap too much
+with specific language model applications nor the general transformer
+architecture, since those are their own distinct topics assigned to 
+other people.
 
@@
 \subsection{Attention masking}
-
-TODO: explain how attention masking works
-
-TODO: explain sparse transformer, used in gpt-3 (maybe 2 also)
+Attention masking prevents the model from attending to some tokens in the input. At any
+given time $j$, the model is allowed to see input up to index $i$. Masking is used to prevent the model from
+attending to future input which would trivialize training. \cite{raffel_exploring_2020}
 
@@
 \cite{vaswani_attention_2017} corresponds to the leftmost masking pattern as
-specified in \ref{masking_patterns}. T5 uses this architecture and masking pattern
+specified in figure \ref{masking_patterns}. T5 uses this architecture and masking pattern
 \cite{raffel_exploring_2020}. As previously mentioned, BERT uses an encoder
@@
 used only for the target language sentence prediction. \cite{raffel_exploring_2020}
+
+Calculating the entire attention history for a long sequence can be an expensive operation.
+It is possible to use a sparse version of the attention masking pattern and still achieve 
+comparable performance to a full attention mask. A sparse transformer with a fixed attention
+pattern includes cells that can summarize the previous locations and propagate 
+that forward. This allows computing longer sequences of input tokens and is used in GPT-3
+\cite{brown_language_2020}. An illustrating example of different masking patterns
+can be seen in figure \ref{sparse_transformer}. \cite{child_generating_2019}
 
@@
 
-TODO: remake, text not visible
 \begin{figure}[h]
@@
   \caption{
+    Sparse Transformer. Visualizing the attention masking pattern on a 6x6 image
+    for two attention heads. On the left, the original transformer. In the middle,
+    a sparse transformer using striding and on the right, a fixed sparse transformer.
     \cite{child_generating_2019}
   }
+\label{sparse_transformer}
 \end{figure}
@@
 
-TODO: talk about masking the attention layers somewhere, was talked about in
-the t5 paper
-TODO: talk about masking, t5 paper lists this as the biggest differentiating factor
-between models. the t5 paper is also good source for general comparison between different
-architectures and approaches
-(the above two are the same)
-
-TODO: talk about the exact differences between fine-tuning,
-i think bert modifies the weights and gpt only adds an extra layer after
-
-TODO: elmo for feature based?
-
-TODO: talk about GPT sparse transformer, used in gpt-3
-
 \subsection{Generative Pre-Trained Transformer}
@@
 
-In the unsupervised pre-training phase, the model is given a set of long form text
-\cite{radford_improving_nodate}. The supervised fine-tuning is used to train the
-model for a specific task.
+In the unsupervised pre-training phase, the model is given a set of long form text. 
+The supervised fine-tuning is used to train the
+model for a specific task. In the supervised fine-tuning phase, an additional linear
+output layer is added
+and the pre-trained model's activation layer and linear output layer are trained
+to the specific task. \cite{radford_improving_nodate}
 
@@
 train the model for specific natural language tasks leveraging the existing language knowledge 
-from the pre-training stage. Fine-tuning is usually a more lightweight operation than pre-training.
+from the pre-training stage. The pre-trained model is used to initialize a new model and 
+then all the parameters are trained for a specific task. Fine-tuning is usually a more 
+lightweight operation than pre-training. \cite{devlin_bert_2019}
 
@@
 \section{Problems}
-TODO: write about hallucination, overconfidence, radicalization etc.
+\subsection{Biases}
+The writers of \cite{brown_language_2020} did a review of gender, racial and religious
+biases in the model they presented in the paper. Their conclusion was that there were
+certain biases in place which matched the biases present in the training data, that being
+the internet.
+
+Most highly educated and physical labor occupations had a male bias and in general, males
+had a bias for being mentioned more often both in positive and negative contexts. Racial
+sentiment depended on the size of the model, but in general, the sentiment for white,
+black and middle eastern people was around neutral and for latinx, asian and indian it was
+positive. For religion, violence was linked to islam at a greater rate than for other
+major world religions.
+
+\subsection{Hallucination}
+Large languge models produce convincing text that can rival human written text \cite{brown_language_2020}.
+It is possible to get these models to produce content which is 
+not entirely factual or even completely nonsensical \cite{ji_survey_2023}.
+
 For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 

### 2023-03-16 paper.tex
Add some corrections

@@
   This paper discusses three language models based on the transformer architecture.
-  I aim decipher some differences between the models which seem very similar at first glance.
+  I aim to decipher some differences between the models which seem very similar at first glance.
   The paper also takes a look at some applications and extensions to basic language
@@
 to using the decoder and encoder stacks of the transformer. GPT uses only
-the decoder, BERT only the encoder and T5 both encoder and decoder
+the decoder, BERT only the encoder and T5 both the encoder and decoder
 \cite{radford_improving_nodate,devlin_bert_2019,raffel_exploring_2020}.
@@
 \section{Training}
-All three of the models this paper discusses use transfer learning for 
+All three of the models this paper discusses use similar approaches for 
 training. The general idea is to first train a baseline model unsupervised 
@@
 in general, a massive number tokens are fed into to model during the course
-of training. Each word corresponds to a single or a few tokens depending on 
+of pre-training. Each word corresponds to a single or a few tokens depending on 
 the encoding used [citation needed, same as pricing] and the number of tokens

### 2023-03-17 paper.tex
Finalized first version

@@
 The three different models are all similar in architecture being mostly
-faithful to the original transformer architecture as presented in 
+faithful to the original transformer as presented in 
 \cite{vaswani_attention_2017}. However, each of them have a different approach
@@
 using a large amount of unstructured text and then fine tuning the model
-for each specific task after.
+for each specific task afterwards.
 
@@
 of pre-training. Each word corresponds to a single or a few tokens depending on 
-the encoding used [citation needed, same as pricing] and the number of tokens
+the encoding used \cite{noauthor_pricing_nodate} and the number of tokens
 used in training can go up to the trillions \cite{raffel_exploring_2020}. 
@@
   }
+  \label{masking_patterns}
 \end{figure}
-\label{masking_patterns}
 
@@
 \cite{vaswani_attention_2017}. Most of the differences between 
-the models come down to training, attention layer masking and the encoder-decoder layers
+the models come down to training, attention layer masking and the use of encoder-decoder layers
 \cite{raffel_exploring_2020}.
@@
 \cite{brown_language_2020}. Depending on the task at hand, it might be sufficient
-to just give the model some examples of the task initially and it will (understand what you want it to do). The examples are given to
+to just give the model some examples of the task initially and it will pick up on the task pattern. The examples are given to
 the model after training during inference and thus differs from fine-tuning. 
@@
 
-As an example \cite{brown_language_2020} used English to French translation.
+As an example, \cite{brown_language_2020} used English to French translation.
 The researchers gave the model between 10 to 100 pairs of examples of the
@@
 The number of examples given is restricted by the size of the model's context,
-which for GPT-3 was 2048 tokens, around 1500 words (citation needed, pricing page has this info).
+which for GPT-3 was 2048 tokens, around 1500 words \cite{noauthor_pricing_nodate}.
 
@@
 
-Next sentence prediction takes a pair of sentences, \texttt{A} and \texttt{B}, and requests the model
+Next sentence prediction takes a pair of sentences, \texttt{A} and \texttt{B}, and asks the model
 to predict whether \texttt{B} follows \texttt{A} or not. In the paper, 50\% of the time \texttt{B} 
@@
 describing the task and outputting the results as text. For example, for STS-B classification
-task the model is trained to out one of a set of floating point numbers 
+task the model is trained to output one of a set of floating point numbers 
 $x \in \{ 1+0.2k \mid k \in \{ 0, 1, ..., 20\} \}$ as a text. Many other models just 
@@
 tasks. Their usefulness quickly diminishes the further we stray from their training set.
-Using multimodal models (check name) however, we can widen the area of tasks the model
+Using multimodal models however, we can widen the area of tasks the model
 can complete and even achieve positive transfer, benefitting from the variety of tasks
@@
 For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
-GPT-3.5 [citation needed], to do a simple calculation, it answers confidently. 
+GPT-3.5 \cite{noauthor_introducing_nodate-1}, to do a simple calculation, it answers confidently. 
 With a prompt of "\texttt{what is 491*397}" we receive a response of 
@@
 The response claims that Sauli Niinistö is currently serving his second term in office
-which is correct as of 2023 and also in 2021 where the training data of GPT-3.5 ends 
-[citation needed]. However, after this, the response claims that his third term began
+which is correct as of 2023 and also in 2021 where the training data of GPT-3.5 ends. 
+However, after this, the response claims that his third term began
 in 2018, directly contradicting the previous statement. It is also important to mention
-that there has been a two term limit since (insert year here) written into law 
-[citation needed, finlex?]. Rest of the response after the first paragraph is removed.
+that there has been a two term limit since the 1990s written into law 
+\cite{oy_finlex_nodate}. Rest of the response after the first paragraph is removed.
 

### 2023-04-13 peer_review/GAN_YeomSong_review.tex
Add peer review stuff

\documentclass[a4paper,11pt]{article}

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{varwidth,xcolor}
\usepackage{graphicx}
\usepackage{amssymb}

\newcommand{\veps}{\varepsilon}
\newcommand{\ee}{{\rm e}\hspace{1pt}}

\begin{document}
\pagestyle{empty}

  \begin{center}
{\large {\bf 
Review on a report \\
``Generative Adversarial Networks'' \\
by Victor Manuel Yeom Song} \\

\bigskip

Written by:

Mikael Fredriksson
 } 
\end{center}

The text is very clearly written. On top of excellent and succint explanations and 
descriptions, graphs and figures are used tastefully when necessary. The paper is 
well balanced between equations, figures and text.

I liked that the concise and exact math definitions were accompanied with more
loose intuitive explanations. This helped me get a rough understanding first and 
then diving into the math was much easier than if there would've been only the
pure math explanations.

As a practical, hands-on guy, I usually prefer to see a bit more examples. In this case,
though, I feel like the distribution of space given to different topics was great.
Explaining the way GANs work and the improvements over the basic implementation takes 
some space and is more important in this case. The organization of the different
topics was very logical, starting from the baseline, explaining the improvements
in chronological order and then talking about examples and conclusions.

I would've hoped to see Jensen-Shannon Divergence explained some more.
The same could probably also be said for Kantorovich-Rubinstein duality but that is
not as important, since it's just a way of getting an equivalent representation
for the loss function which is more easily optimized. Jensen-Shannon Divergence, on
the other hand, was directly an inseparable part of the minimized function. Then
again, the point of the paper is to be explain GANs and not teach math.

The conclusion is short, simple and to the point. It recaps the topics discussed and
offers quite generic commentary on the popularity of GANs.

Overall, the text was a pleasure to read. I feel like it gave me a good overview
of the inner workings of GANs and serves a good foundation to continue reading further.

As a last note, I noticed a slight typo in the beginning:

\begin{itemize}

	\item First sentence in the abstract, machine learning is misspelled missing an n.

\end{itemize}

\end{document}

### 2023-04-13 peer_review/model-free-reinforcement-learning_kinnunen_review.tex
Add peer review stuff

--- 2023-04-13 peer_review/GAN_YeomSong_review.tex
@@
 Review on a report \\
-``Generative Adversarial Networks'' \\
-by Victor Manuel Yeom Song} \\
+``Title of the report'' \\
+by Report Author} \\
 
@@
 
-Mikael Fredriksson
  } 
@@
 
-The text is very clearly written. On top of excellent and succint explanations and 
-descriptions, graphs and figures are used tastefully when necessary. The paper is 
-well balanced between equations, figures and text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
+Text text text text text text text text text text text text text text text text text text text text text text.
 
-I liked that the concise and exact math definitions were accompanied with more
-loose intuitive explanations. This helped me get a rough understanding first and 
-then diving into the math was much easier than if there would've been only the
-pure math explanations.
-
-As a practical, hands-on guy, I usually prefer to see a bit more examples. In this case,
-though, I feel like the distribution of space given to different topics was great.
-Explaining the way GANs work and the improvements over the basic implementation takes 
-some space and is more important in this case. The organization of the different
-topics was very logical, starting from the baseline, explaining the improvements
-in chronological order and then talking about examples and conclusions.
-
-I would've hoped to see Jensen-Shannon Divergence explained some more.
-The same could probably also be said for Kantorovich-Rubinstein duality but that is
-not as important, since it's just a way of getting an equivalent representation
-for the loss function which is more easily optimized. Jensen-Shannon Divergence, on
-the other hand, was directly an inseparable part of the minimized function. Then
-again, the point of the paper is to be explain GANs and not teach math.
-
-The conclusion is short, simple and to the point. It recaps the topics discussed and
-offers quite generic commentary on the popularity of GANs.
-
-Overall, the text was a pleasure to read. I feel like it gave me a good overview
-of the inner workings of GANs and serves a good foundation to continue reading further.
-
-As a last note, I noticed a slight typo in the beginning:
+However, I do have some suggestions for corrections,
+described in more detail below:
 
@@
 
-	\item First sentence in the abstract, machine learning is misspelled missing an n.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Text text text text text text text text text text text text text text text text text text text text text text.
 

### 2023-04-13 peer_review/model-free-reinforcement-learning_kinnunen_review.tex
Add some comments to reinforcement learning

@@
 Review on a report \\
-``Title of the report'' \\
-by Report Author} \\
+``Model-free deep reinforcement learning'' \\
+by Anniina Kinnunen} \\
 
@@
 
+Mikael Fredriksson
  } 
@@
 
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
-Text text text text text text text text text text text text text text text text text text text text text text.
+As the paper is currently as short as it is, it will be quite difficult to give 
+adequate feedback. I'll try my best, though.
 
-However, I do have some suggestions for corrections,
-described in more detail below:
+The structure seems sound when looking at the currently existing text and the planned
+additions. The text is quite clear and visuals and the one equation help in understanding.
+Thank you for explaining thoroughly what everything means in the equation.
+
+The basic description of reinforcement learning is clear. You could maybe consider
+whether adding some equations would make it even clearer but it's already good as it is.
+
+Additionally, I listed some ideas for possible corrections below:
 
@@
 
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
-	\item Text text text text text text text text text text text text text text text text text text text text text text.
+	\item Claiming that there are exactly three categories of machine learning 
+		  is somewhat questionable in my opinion. I would personally use a more
+		  vague statement such as "reinforcement learning is one of the categories of
+		  machine learning, which include e.g. unsupervised and supervised learning".
+		  Depending on the source, you could argue semi-supervised learning being its
+		  own category. I even saw some claiming deep learning being its own category.
+		  Generally I usually try to avoid such sweeping statements about large
+		  fields like machine learning.
 

### 2023-04-28 paper.tex
Remove 'for the reader' section

@@
 \addbibresource{references.bib}
-
-% TODO: temporary for having the "for the reader" section start from 0
-\setcounter{section}{-1}
 
@@
 \end{abstract}
-
-\section{For the reader}
-There's a bit of length left in this paper for some extra explanations,
-examples and images, so if there's anything specific you would like to
-read about, please indicate that in your review. It can be quite hard to 
-gauge the level of difficulty of different topics after being submerged 
-in them for a while. Please keep in mind that I should not overlap too much
-with specific language model applications nor the general transformer
-architecture, since those are their own distinct topics assigned to 
-other people.
 

### 2023-04-28 paper.tex
Make some proposed changes, add to intro, write conclusion

@@
 \section{Introduction}
+
+TODO: write a generic paragraph
+
+Transformers can be split into two main parts: an encoder and a decoder stack. 
+The encoder reads the input text converting it into a vector representation. This is
+then fed into the decoder which then generates the output utilizing this vector.
+It is not necessary to have both an encoder and a decoder in the transformers
+and the same tasks can be performed even without one of these present.
+
+While encoder-decoder language models existed before the transformer, it was 
+the first one to use only an attention mechanism for all computation. 
+The attention mechanism is a mapping for a query and key-value pairs to some output. 
+Intuitively, in transformers
+it is used by the model to give different weights for different words in the input when
+determining what the output should be [TODO: citation needed].
+
 This paper will take a look at three popular language models utilizing
@@
 
-The three different models are all similar in architecture being mostly
-faithful to the original transformer as presented in 
+The three different models studied in this paper are all similar in architecture 
+being mostly faithful to the original transformer as presented in 
 \cite{vaswani_attention_2017}. However, each of them have a different approach
@@
 general language understanding. The exact details between models varies but
-in general, a massive number tokens are fed into to model during the course
+in general, a massive number of tokens are fed into the model during the course
 of pre-training. Each word corresponds to a single or a few tokens depending on 
@@
 \subsection{Attention masking}
-Attention masking prevents the model from attending to some tokens in the input. At any
-given time $j$, the model is allowed to see input up to index $i$. Masking is used to prevent the model from
-attending to future input which would trivialize training. \cite{raffel_exploring_2020}
+Attention masking prevents the model from seeing some tokens in the input. At any
+given time $j$, the model is allowed to use input up to index $i$. Masking is used to prevent the model from
+seeing future input which would trivialize training. \cite{raffel_exploring_2020}
 
@@
 \cite{vaswani_attention_2017} corresponds to the leftmost masking pattern as
-specified in figure \ref{masking_patterns}. T5 uses this architecture and masking pattern
+specified in Figure \ref{masking_patterns}. T5 uses this architecture and masking pattern
 \cite{raffel_exploring_2020}. As previously mentioned, BERT uses an encoder
@@
 \cite{brown_language_2020}. An illustrating example of different masking patterns
-can be seen in figure \ref{sparse_transformer}. \cite{child_generating_2019}
+can be seen in Figure \ref{sparse_transformer}. \cite{child_generating_2019}
 
@@
 
-As an example, \cite{brown_language_2020} used English to French translation.
+As an example, Brown et al. \cite{brown_language_2020} used English to French translation.
 The researchers gave the model between 10 to 100 pairs of examples of the
@@
 While few-shot learning requires less data and computing power, which makes it more
-accessible compared to fine-tuning a large model, at least during the writing of 
-\cite{brown_language_2020} failed to produce comparable results to fine-tuning.
+accessible compared to fine-tuning a large model, Brown et al. \cite{brown_language_2020} 
+were unable to produce comparable results to fine-tuning.
 The number of examples given is restricted by the size of the model's context,
@@
 \subsection{Bidirectional Encoder Representations from Transformers}
-Bidirectional Encoder Representations from Transformers, henceforth referred to as BERT,
+Bidirectional Encoder Representations from Transformers (BERT)
 is a language model utilizing masking of words during training to achieve bidirectionality
@@
 two different training approaches are used: masked language model and next sentence prediction.
-Masking allows the self-attention layer to take into account both sides of a given word, instead
-of just one side, as in GPT which can only use the previous words as context. Using next sentence
+Word masking allows the self-attention layer to take into account both sides of a given word, instead
+of just one side, as in GPT which can only use the previous words as context. Word masking is
+distinct from attention masking and refers to the hiding of individual words in the training data
+before feeding it into the model.
+% TODO: verify this
+ Using next sentence
 prediction improves the model's understanding of the relationships between sentences. This is
@@
 
-A masked language model (MLM) is achived by hiding a certain number of tokens, 12\% in the paper, and
+A masked language model (MLM) is achived by hiding a certain number of tokens and
 asking the model to predict the hidden token. The model can then use both sides of the token as
@@
 tailoring each output to the specific task at hand, every task takes in a text prefix
-describing the task and outputting the results as text. For example, for STS-B classification
+describing the task and outputting the results as text. For example, for a classification
 task the model is trained to output one of a set of floating point numbers 
-$x \in \{ 1+0.2k \mid k \in \{ 0, 1, ..., 20\} \}$ as a text. Many other models just 
+$x \in \{ 1+0.2k \mid k \in \{ 0, 1, ..., 20\} \}$ as text. Many other models just 
 output a number directly as a sliding scale from 1 to 5.
 
-\section{Applications}
+\section{Extensions}
 
@@
 \subsection{Biases}
-The writers of \cite{brown_language_2020} did a review of gender, racial and religious
+Brown et al. \cite{brown_language_2020} did a review of gender, racial and religious
 biases in the model they presented in the paper. Their conclusion was that there were
@@
 
+\section{Conclusion}
+This paper introduced three popular language models based on the transformer architecture.
+They are mostly similar, all faithful to the original transformer architecture, with
+some key differences in the usage of attention masking and encoder-decoder stacks.
+
+Transformers are able to produce impressive results on many different domains of natural
+language processing. However, it is important to keep in mind that they are not without 
+their problems. As with any machine learning model,
+biases should be considered and the outputs validated.
+
+Hopefully this paper serves as a good introduction to the general landscape of 
+transformers in language models and helps in understanding what is going on in
+large language models.
+
 \printbibliography

### 2023-05-06 paper.tex
Make corrections

@@
 
-TODO: write a generic paragraph
+Natural language processing has increased in popularity. As the amount of textual data
+increases, companies and researchers are looking for better ways of getting insights from
+these sources. Transformers offer an answer
+to the ever increasing requirements.
 
@@
 and the same tasks can be performed even without one of these present. 
+\cite{vaswani_attention_2017}
 
@@
 it is used by the model to give different weights for different words in the input when
-determining what the output should be [TODO: citation needed].
+determining what the output should be. \cite{galassi_attention_2021}
 
@@
 
-The three different models studied in this paper are all similar in architecture 
+The three different models studied in this paper, GPT, BERT and T5, are all similar in architecture 
 being mostly faithful to the original transformer as presented in 
@@
 training. The general idea is to first train a baseline model unsupervised 
-using a large amount of unstructured text and then fine tuning the model
+using a large amount of written text and then fine tuning the model
 for each specific task afterwards.
@@
 
-In the fine-tuning stage, the pre-trained model is used as a baseline. A new
-model is trained using supervised learning with a task specific data set. 
+In the fine-tuning stage, the pre-trained model is adapted to a specific task 
+using supervised learning.
 The training can fine-tune all the parameters of the model, as in BERT 
@@
 seeing future input which would trivialize training. \cite{raffel_exploring_2020}
+
+Some common masking patterns include fully-visible, causal and causal with prefix.
+Figure \ref{masking_patterns_raw} offers a helpful visualization for these three
+patterns. 
+The patterns can be mixed together and different parts of the transformer can use different
+masking patterns.
 
@@
 
-Prefix masking can be useful for example when translating. The prefix allows the
+Prefix masking, which corresponds to the rightmost masking pattern in Figure 
+\ref{masking_patterns}, can be useful for example when translating. The prefix allows the
 model to attend to the entire source language sentence and causal masking can be 
-used only for the target language sentence prediction. \cite{raffel_exploring_2020}
+used only for the target language sentence prediction. For example when translating, given an input
+such as \texttt{[BEGIN]The dog is red.[PAD][SEP]Koira on punainen.[END]}, prefix masking 
+can allow the model to fully attend to the input up until \texttt{[SEP]}. Only after this
+point does the model have to start generating an output of its own.
+ \cite{raffel_exploring_2020}
 
@@
     Light squares indicate that the access is blocked for a given pair $i$, $j$. 
-    \cite{raffel_exploring_2020}
+    Figure by Raffel et al. \cite{raffel_exploring_2020}
   }
+  \label{masking_patterns_raw}
 \end{figure}
@@
     fully-visible masking. Light gray lines indicate causal masking.
-    \cite{raffel_exploring_2020}
+    Figure by Raffel et al. \cite{raffel_exploring_2020}
   }
@@
     a sparse transformer using striding and on the right, a fixed sparse transformer.
-    \cite{child_generating_2019}
+    Figure by Child et al. \cite{child_generating_2019}
   }
@@
 is a language model utilizing masking of words during training to achieve bidirectionality
-in the model. \cite{devlin_bert_2019}
+in the model. Bidirectionality allows the model to simultaneously take into account
+both sides of the processed word, while a generic transformer can only see one. \cite{devlin_bert_2019}
 
@@
   \end{tikzpicture}
-  \caption{Illustrating the types of inputs and outputs. Recreated from \cite{raffel_exploring_2020}.}
+  \caption{Illustrating the types of inputs and outputs. Recreated from a Figure by Raffel et al. \cite{raffel_exploring_2020}.}
 \end{figure*}
@@
 Large language models have proven themselves very capable at a variety of language related
-tasks. Their usefulness quickly diminishes the further we stray from their training set.
+tasks. Unfortunately, their usefulness quickly diminishes the further we stray from their training set.
 Using multimodal models however, we can widen the area of tasks the model
@@
     distinct robotics domains when trained together than when trained separately for the 
-    specific tasks. \cite{driess_palm-e_2023}
+    specific tasks. Figure by Driess et al. \cite{driess_palm-e_2023}
   }

### 2023-05-07 paper.tex
Final few changes

@@
 used only for the target language sentence prediction. For example when translating, given an input
-such as \texttt{[BEGIN]The dog is red.[PAD][SEP]Koira on punainen.[END]}, prefix masking 
+such as \texttt{[BEGIN]The dog is red.[SEP]Koira on punainen.[END]}, prefix masking 
 can allow the model to fully attend to the input up until \texttt{[SEP]}. Only after this
@@
 Hopefully this paper serves as a good introduction to the general landscape of 
-transformers in language models and helps in understanding what is going on in
-large language models.
+transformers in language models and helps in understanding what is going on 
+under the hood in large language models.
 
